\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{listings}
\usepackage{array}

\definecolor{instrNavy}{HTML}{1F3864}
\definecolor{instrTeal}{HTML}{0D9488}
\definecolor{instrAmber}{HTML}{D97706}
\definecolor{instrIndigo}{HTML}{4F46E5}
\definecolor{instrGreen}{HTML}{15803D}
\definecolor{instrOrange}{HTML}{C2410C}
\definecolor{instrKeyBody}{HTML}{DBEAFE}
\definecolor{instrAskBody}{HTML}{EEF2FF}
\definecolor{instrDemoBody}{HTML}{DCFCE7}
\definecolor{instrThesisBody}{HTML}{FFEDD5}

% Talking points environment - amber, instructor voice
\newmdenv[
  backgroundcolor=instrAmber!15,
  linecolor=instrAmber,
  linewidth=2pt,
  innerleftmargin=8pt,
  innerrightmargin=8pt,
  innertopmargin=6pt,
  innerbottommargin=6pt,
  skipabove=8pt,
  skipbelow=4pt
]{talkingpointsenv}

% Hook block - teal, "start here"
\newmdenv[
  backgroundcolor=instrTeal!15,
  linecolor=instrTeal,
  linewidth=2pt,
  innerleftmargin=8pt,
  innerrightmargin=8pt,
  innertopmargin=6pt,
  innerbottommargin=6pt,
  skipabove=8pt,
  skipbelow=4pt
]{hookenv}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textbf{Virtual Memory and Paging}}
\fancyhead[R]{\small\textbf{CECS 326 — Operating Systems}}
\fancyfoot[C]{\small Page \thepage}
\renewcommand{\headrulewidth}{0.4pt}

\setlist[itemize]{noitemsep, topsep=4pt, leftmargin=1.5em}
\setlist[enumerate]{noitemsep, topsep=4pt, leftmargin=1.5em}

\lstset{
  basicstyle=\ttfamily\small,
  backgroundcolor=\color{black!5},
  frame=single,
  framesep=4pt,
  breaklines=true,
  columns=flexible,
}

\begin{document}
\thispagestyle{fancy}

{\color{instrNavy}\LARGE\textbf{Virtual Memory and Paging}}\\[0.3em]
{\large\textit{Study Questions}}\\[0.1em]
{\normalsize CECS 326 — Operating Systems}\\[0.5em]
{\color{instrNavy}\rule{\linewidth}{1.5pt}}
\vspace{0.5em}

\noindent\textit{These questions reinforce the lecture and guided notes. They should deepen recall and transfer — not a substitute for attending.}


{\color{instrNavy}\large\textbf{Recall}}
{\color{instrNavy}\rule{\linewidth}{0.4pt}}

\noindent\textbf{Q1.} Define Virtual address space.

\vspace{2em}

\noindent\textbf{Q2.} Summarize the main idea behind Page table translation.

\vspace{2em}


{\color{instrNavy}\large\textbf{Apply}}
{\color{instrNavy}\rule{\linewidth}{0.4pt}}

\noindent\textbf{Q3.} Apply Virtual address space to one of today’s case studies.

\vspace{3em}

\noindent\textbf{Q4.} Explain how Why Virtual Memory Exists would change under a different workload or constraint.

\vspace{3em}

\noindent\textbf{Q5.} Choose one tradeoff from the lecture and defend a decision.

\vspace{3em}


{\color{instrNavy}\large\textbf{Analyze}}
{\color{instrNavy}\rule{\linewidth}{0.4pt}}

\noindent\textbf{Q6.} Compare two approaches from the lecture and identify the stronger fit for a real system.

\vspace{4em}

\noindent\textbf{Q7.} Identify the failure mode most likely to appear if the lecture’s guardrails are ignored.

\vspace{4em}

\noindent\textbf{Q8.} Evaluate how the lecture’s design choices affect observability, performance, and correctness.

\vspace{4em}

\noindent\textbf{Q9.} Build a short argument connecting the framework to an unfamiliar scenario.

\vspace{4em}

\noindent\textbf{Q10.} Critique the lecture’s case study and propose a better alternative.

\vspace{4em}

\end{document}
